Correlation of filter methods

### 2020-01-15 analysis/filter-correlation.Rmd
wflow_publish(knitr_in("analysis/filter-correlation.Rmd"), view = FALSE, verbose = TRUE)

fv_all <- dplyr::bind_rows(
  fv_vi_car$data,
  fv_vi_info.gain$data,
  fv_vi_gain.ratio$data,
  fv_vi_symuncert$data,
  fv_vi_relief$data,
  fv_vi_rank$data,
  fv_vi_cor$data,
  fv_vi_mrmr$data,
  fv_vi_cmim$data,
  fv_vi_var$data
) %>%
  dplyr::select(value, method) %>%
  mutate(id = rep(1:89, 10)) %>%
  tidyr::spread(method, value) %>%
  mutate_if(is.numeric, list(~ na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% # NA in cmim
  dplyr::select(-id)

@@

```{r correlation-nbins, warning=FALSE, dev = c("png", "pdf")}
# recode levels so that they are unique
fv_all_list <- map2(
  list(
    fv_vi_info.gain5$data, fv_vi_info.gain10$data,
    fv_vi_info.gain15$data, fv_vi_info.gain20$data,
    fv_vi_info.gain25$data, fv_vi_info.gain30$data
  ),
  list(5, 10, 15, 20, 25, 30), ~
  dplyr::mutate(.x, method = recode(.x$method, FSelectorRcpp_information.gain = glue("FSelectorRcpp_information.gain-{.y}")))
)

fv_all <- dplyr::bind_rows(
  fv_all_list
) %>%
  dplyr::select(value, method) %>%
  mutate(id = rep(1:89, 6)) %>%
  tidyr::spread(method, value) %>%
  mutate_if(is.numeric, list(~ na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>%
  dplyr::select(-id)

@@

fv_all <- dplyr::bind_rows(
  fv_nri_car$data,
  fv_nri_info.gain$data,
  fv_nri_gain.ratio$data,
  fv_nri_symuncert$data,
  fv_nri_relief$data,
  fv_nri_rank$data,
  fv_nri_cor$data,
  fv_nri_mrmr$data,
  fv_nri_cmim$data,
  fv_nri_var$data
) %>%
  dplyr::select(value, method) %>%
  mutate(id = rep(1:7381, 10)) %>%
  tidyr::spread(method, value) %>%
  dplyr::select(-id)

@@

fv_all <- dplyr::bind_rows(
  fv_hr_car$data,
  fv_hr_info.gain$data,
  fv_hr_gain.ratio$data,
  fv_hr_symuncert$data,
  fv_hr_relief$data,
  fv_hr_rank$data,
  fv_hr_cor$data,
  fv_hr_mrmr$data,
  fv_hr_cmim$data,
  fv_hr_var$data
) %>%
  dplyr::select(value, method) %>%
  mutate(id = rep(1:122, 10)) %>%
  tidyr::spread(method, value) %>%
  dplyr::select(-id)

>>>>

fv_all <- dplyr::bind_rows(
  fv_vi_car$data,
  fv_vi_info.gain$data,
  fv_vi_gain.ratio$data,
  fv_vi_symuncert$data,
  fv_vi_relief$data,
  fv_vi_rank$data,
  fv_vi_cor$data,
  fv_vi_mrmr$data,
  fv_vi_cmim$data,
  fv_vi_var$data
) %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:89, 10)) %>%
  tidyr::spread(filter, value) %>%
  mutate_if(is.numeric, list(~ na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% # NA in cmim
  dplyr::select(-id)

@@

```{r correlation-nbins, warning=FALSE, dev = c("png", "pdf")}
# recode levels so that they are unique
fv_all_list <- map2(
  list(
    fv_vi_info.gain5$data, fv_vi_info.gain10$data,
    fv_vi_info.gain15$data, fv_vi_info.gain20$data,
    fv_vi_info.gain25$data, fv_vi_info.gain30$data
  ),
  list(5, 10, 15, 20, 25, 30), ~
  dplyr::mutate(.x, filter = recode(.x$filter, FSelectorRcpp_information.gain = glue("FSelectorRcpp_information.gain-{.y}")))
)

fv_all <- dplyr::bind_rows(
  fv_all_list
) %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:89, 6)) %>%
  tidyr::spread(filter, value) %>%
  mutate_if(is.numeric, list(~ na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>%
  dplyr::select(-id)

@@

fv_all <- dplyr::bind_rows(
  fv_nri_car$data,
  fv_nri_info.gain$data,
  fv_nri_gain.ratio$data,
  fv_nri_symuncert$data,
  fv_nri_relief$data,
  fv_nri_rank$data,
  fv_nri_cor$data,
  fv_nri_mrmr$data,
  fv_nri_cmim$data,
  fv_nri_var$data
) %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:7381, 10)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

@@

fv_all <- dplyr::bind_rows(
  fv_hr_car$data,
  fv_hr_info.gain$data,
  fv_hr_gain.ratio$data,
  fv_hr_symuncert$data,
  fv_hr_relief$data,
  fv_hr_rank$data,
  fv_hr_cor$data,
  fv_hr_mrmr$data,
  fv_hr_cmim$data,
  fv_hr_var$data
) %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:122, 10)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)
